### 2018-09-17 manuscript/methods.tex
small tex matters

\subsection{Models}
We first defined a binary state speciation and extinction model (BiSSE, \citet{maddison_2007})  for polyploidy evolution where taxa was classified as diploid (D=0) and polyploid (P=1) \ref{datatable}. In  a Bayesian framework, we obtained posterior probability distributions of speciation rates ($\lambda_D$, $\lambda_P$), extinction rates ($\mu_D$, $\mu_P$) , net diversification rates ($r_D=\lambda_D-\mu_D, r_P=\lambda_P-\mu_P$), and  relative extinction rates ($\nu_D=\frac{\mu_D}{\lambda_D}, \nu_D=\frac{\mu_D}{\lambda_D}$) just as previously explored in \citet{mayrose_2011}. The cladogenetic changes explored in BiSSE were polyploidization rate are represented by parameter $\rho$ and by diploidization parameter rate $\delta$.\newline

@@

For breeding system both BiSSE and a HiSSE models were fitted independently by coding data as self-compatible (SC=0) or self-incompatible (SI=1) \ref{datatable}. The BiSSE model fitted to breeding system data was done with the goal of investigating if the effect of self-incompatibility in diversification was similar to the pattern found by  \citet{goldberg_2012}. However, the HiSSE model on breeding system parses out if the effect of breeding system in diversification is significant  by minimizing type I error as mentioned above. For these models we assumed that self-compatibility is irreversible as discussed by \citet{igic_2013}, so we defined the transition rate $q_{IC}$ as the parameter for changes from self-incompatible to self-compatible state.\newline

Next, we proposed a multivariate speciation and extinction model (MuSSE, \citet{fitzjohn_2012}) to investigate the link amongst diversification, breeding system, and polyploidy simultaneously. The MuSSE model is defined using three states self-compatible diploids (SC-D=0), polyploids that are always self-compatible (ref for this??) (P=1), and self-incompatible diploids (SI-D=2, see table \ref{datatable}) and contains ten parameters, six defining diversification ($\lambda_{SD}, \mu_{SD},\lambda_{P},\mu_{P}, \lambda_{ID},\mu_{ID}$) and the other four key cladogenetic changes that are: polyploidization of self-compatible diploids $\rho_{SD}$, diploidization $\delta$, polyploidization of self-incompatible diploids $\rho_{ID}$, and self-incompatible to self-compatible rate $q_{IC}$.\newline

@@

\noindent \begin{tabular}{@{}llccc@{}} \toprule %\label{datatable}
%  \caption{Binary and three state classifications for 595 taxa with ploidy and/or breeding system data. The number of taxa in the t he sample was maximize by including tips with only ploidy or only breeding system and assigned them as uncertain in the unknown character.}
\multicolumn{4}{r}{Models} \\ \cmidrule(r){3-5}
Type & Total of & BiSSE/HiSSE & BiSSE/HiSSE & MuSSE/MuHiSSE\\ 
 &Taxa &  Polyploidy & Breeding System &  \\ \midrule
Diploid Self Compatible & 152 & 0 &  0 & 0 \\
Diploid Self Incompatible& 97 & 0  & 1 & 2\\
Diploid with unknown breeding system & 219 & 0 & (0,1) & (0,2) \\
Polyploid & 81 & 1& 0 & 1 \\
Unknow ploidy and self compatible& 34 & (0,1)& 0 & (0,1) \\ 
Unknown ploidy and self incompatible & 12 & 0 & 1 & 2 \\ \bottomrule
\end{tabular}

>>>>

\subsection{Models}
We first defined a binary state speciation and extinction model (BiSSE, \citet{maddison_2007})  for polyploidy evolution where taxa was classified as diploid (D=0) and polyploid (P=1) \cref{table:datatable}. In  a Bayesian framework, we obtained posterior probability distributions of speciation rates ($\lambda_D$, $\lambda_P$), extinction rates ($\mu_D$, $\mu_P$) , net diversification rates ($r_D=\lambda_D-\mu_D, r_P=\lambda_P-\mu_P$), and  relative extinction rates ($\nu_D=\frac{\mu_D}{\lambda_D}, \nu_D=\frac{\mu_D}{\lambda_D}$) just as previously explored in \citet{mayrose_2011}. The cladogenetic changes explored in BiSSE were polyploidization rate are represented by parameter $\rho$ and by diploidization parameter rate $\delta$.\newline

@@

For breeding system both BiSSE and a HiSSE models were fitted independently by coding data as self-compatible (SC=0) or self-incompatible (SI=1) \cref{table:datatable}. The BiSSE model fitted to breeding system data was done with the goal of investigating if the effect of self-incompatibility in diversification was similar to the pattern found by  \citet{goldberg_2012}. However, the HiSSE model on breeding system parses out if the effect of breeding system in diversification is significant  by minimizing type I error as mentioned above. For these models we assumed that self-compatibility is irreversible as discussed by \citet{igic_2013}, so we defined the transition rate $q_{IC}$ as the parameter for changes from self-incompatible to self-compatible state.\newline

Next, we proposed a multivariate speciation and extinction model (MuSSE, \citet{fitzjohn_2012}) to investigate the link amongst diversification, breeding system, and polyploidy simultaneously. The MuSSE model is defined using three states self-compatible diploids (SC-D=0), polyploids that are always self-compatible (ref for this??) (P=1), and self-incompatible diploids (SI-D=2, see table \cref{table:datatable}) and contains ten parameters, six defining diversification ($\lambda_{SD}, \mu_{SD},\lambda_{P},\mu_{P}, \lambda_{ID},\mu_{ID}$) and the other four key cladogenetic changes that are: polyploidization of self-compatible diploids $\rho_{SD}$, diploidization $\delta$, polyploidization of self-incompatible diploids $\rho_{ID}$, and self-incompatible to self-compatible rate $q_{IC}$.\newline

@@

\begin{table}
\begin{tabular}{@{}llccc@{}} \toprule
\multicolumn{4}{r}{Models} \\ \cmidrule(r){3-5}
Type & Total of & BiSSE/HiSSE & BiSSE/HiSSE & MuSSE/MuHiSSE\\ 
 &Taxa &  Polyploidy & Breeding System &  \\ \midrule
Diploid Self Compatible & 152 & 0 &  0 & 0 \\
Diploid Self Incompatible& 97 & 0  & 1 & 2\\
Diploid with unknown breeding system & 219 & 0 & (0,1) & (0,2) \\
Polyploid & 81 & 1& 0 & 1 \\
Unknow ploidy and self compatible& 34 & (0,1)& 0 & (0,1) \\ 
Unknown ploidy and self incompatible & 12 & 0 & 1 & 2 \\ \bottomrule
\end{tabular}
\caption{Binary and three state classifications for 595 taxa with ploidy and/or breeding system data. The number of taxa in the t he sample was maximize by including tips with only ploidy or only breeding system and assigned them as uncertain in the unknown character.}
\label{table:datatable}
\end{table}
